I/O simulation model with Linux page cache, integration and evaluation in SimGrid framework

### 2020-07-03 paper_io_sim.tex
edits and comments in methods

		\subsection{Page cache}
			\begin{itemize}
				\item What is page cache? How it works \cite{linuxdev3rd2010}. Effects and importance of page cache.
				\item Introduce some existing strategies with some highlighted pros and cons.
				\item Current implementation in Linux and some reasons why it is chosen to be implemented (implementation complexity, effectiveness, overhead, etc) \cite{linuxdev3rd2010}
			\end{itemize}

		\subsection{Simulators}
			\begin{itemize}
				\item Discuss some existing methods, simulation frameworks to conduct HPC experiments. Compare pros and cons (accuracy, simulation time, usability) of some simulators (SimGrid, GridSim).
				\item Related development: RAM energy consumption \cite{gill2019} \cite{ouarnoughi2017} 
				\item Discuss the pros of SimGrid and the reasons why we chose it to extend. (Section 2.2.2 in \cite{casanova2014})
			\end{itemize}

	\section{Method}
		In this section, we present our approach to model file read/write, 
		I/O in memory, data flushing and cache eviction mechanisms 
		implemented in the Linux kernel. 
		We also detail the design of the simulators in order to simulate 
		I/O activities and the implementation in Python and SimGrid framework. 
		Finally, we describe experimental scenarios to evaluate our model using 
		real applications and a Python simulator prototype, the current SimGrid 
		simulator, our extension of SimGrid, and the results from real pipelines.

@@

			Our simulation model simulates the main mechanisms of the
			write-back page cache including memory I/O, cache eviction and
			data flushing. We separate our model in two components, the IO
			Controller and the Memory Manager, which together simulate I/O
			in the Linux kernel (Figure~\ref{fig:interaction}). The Memory
			Manager simulates memory I/O, flushing, and cache eviction, whereas the
			IO Controller simulates file read and file write.
			Simulated applications can simply request
			file reads and file writes from the IO Manager
			instead of calling simulated storage directly.

@@

			Memory can be characterized with a capacity, read bandwidth and write 
			bandwidth. However, memory bandwidth is always shared between 
			concurrent processes and implementing a simulation model of concurrent 
			accesses to memory is non-trivial. Thus, we leverage existing storage 
			models, which handle parallel storage accesses, in some simulation 
			frameworks to simulate I/O time in memory.

			We introduce the concept of data block as a unit to represent cached data. 
			A data block is a subset of pages of a file in page cache that is accessed 
			at a specific time. Therefore, a block has the information about file name, 
			block size, last access and a dirty flag with values of 0 and 1, 
			0 represents block of lean data, while 1 indicates that the data block 
			is dirty. 
			Cached data of a file can be represented by multiple blocks. 
			Because a data block represents a subset of cached pages, 
			it can be split into smaller blocks, and multiple blocks can also 
			be merged into a larger one.

			In Linux kernel, the page cache LRU lists are lists of pages of 
			files in cache. In our simulator, instead of using lists of pages, 
			we simulate these lists with two lists of data blocks, an active list and 
			an inactive list, ordered by block last access as is shown in 
			Figure~\ref{fig:lrulist}.
			As in the kernel, in our simulator, we keep the size of the active list not 
			larger than twice the size of the inactive list by moving least recently 
			used blocks from the active list to the inactive list.

@@

			Modeling page cache LRU lists as lists of blocks offers our simulator 
			some obvious advantages. 
			Maintaining and handling lists of pages in the simulator, which is in 
			packet level, are non-trivial when they require significant implementation 
			overhead and would likely to hinder the performance of the simulator. 
			Therefore, using page cache lists of data blocks can simplify the 
			simulation of cache eviction and data flushing while preserving
			the accuracy in i/o time simulation.

			With the simulation model of page cache LRU lists of blocks, now we can 
			model I/O in memory.
			At the time when a file is accessed, some data of the file can be in 
			cache or not. 
			If accessed data is already cached, there are existing data blocks 
			representing cached data in two page cache LRU lists. 
			As cached data is accessed again, these blocks are moved to 
			the active list, dirty blocks are merged into a bigger dirty block, 
			while clean data blocks are merged into another clean block. 
			If accessed data is not in cache, new blocks representing uncached data 
			are created and put into the top of the inactive list. 
			For more detail when uncached data is accessed, in the case of 
			reading file, as all uncached data is clean data, only one clean data 
			block is added to the inactive list.
			But in the case of writing uncached file data though cache, 
			this written data can be either dirty or clean. 
			Thus, at most two data blocks can be added to the inactive lists, 
			one is clean and one is dirty. 
			We also keep the size of the active list not larger than twice the size of 
			the inactive list as in the kernel. This is done by moving least recently 
			used blocks in the active list to the inactive list when the active list 
			grows. If only a part of a data block needs to be moved, 
			the block is split.

			Next, we simulate data flushing mechanism, which writes back 
			dirty data to disk. 
			The data flushing simulation function traverses the sorted inactive first, 
			and then the active list, looks for least recently used dirty blocks and 
			sets dirty flags of these blocks to 0 until the total flushed amount 
			reaches the amount to be flushed or there is no dirty data left in cache. 
			If the last flushed block is not entirely flushed, it is split into 
			two blocks, one is flushed and one remains dirty.
			The flushing time is simulated with storage model.

			For periodical flushing, our simulator searches in two page cache 
			LRU lists and flushes all the expired dirty data blocks. 
			A dirty data block is considered expired if the time from its last access 
			to current simulated time is longer than the predefined expire time. 
			Periodical flushing can be concurrent with cache read/write, 
			and sequential with disk read/write. When cache accesses and 
			periodical flushing are concurrent, flushing time is not added to simulated 
			time but the amount of flushed data is limited by flushing time. 
			When data is flushed in parallel with disk read/write, flushing time is 
			calculated by storage simulation model and total amount of data 
			to be flushed.

@@

@@

			Simulated applications can simply request for a file read 
			or file write by calling the APIs of this layer instead of 
			calling directly to storage simulation models.
			Because every computer has its own memory and system configurations, 
			one IOController object and one MemoryManager object are created 
			for each simulated machine.

			To read or write a file, a simulated application sends a request to the 
			IOController instance on the node where the requested file is stored.
			Based on the memory status in MemoryManager, the IOController 
			orchestrates cache read/write, disk read/write, flushing and cache eviction 
			to fulfill I/O requests, calculates total simulated time and returns to 
			simulated applications.

@@

			The algorithm used to simulate file read is described in 
			Algorithm~\ref{alg:read}. 
			In Linux systems with write back storage devices, data can be either read 
			from cache with memory bandwidth or read from disk with disk bandwidth. 
			Therefore, total read time can be considered as a linear function 
			of the read time with each of these bandwidths, 
			enabling us to generalize reading process as two separate phases, 
			cache read and disk read. 
			When a user simulated application reads a file, 
			it sends a file read request to IOController. 
			First, dirty data is flushed to disk to make more available memory 
			to read the file if needed.
			Data flushing function in MemoryManager is called, flushing time is 
			simulated and added to total run time (line 10).
			After data is flushed, MemoryManager is asked to evict data 
			from cache to accommodate the requested file (line 11). 
			Next, if file is cached either partially or entirely, MemoryManager is 
			called to re-access and update this cached data (line 13). 
			During cache read, periodical flushing is called to flush dirty data if needed 
			and limited to cache read time (line 14).
			Cache read time is then added to total simulated time (line 15). 
			If file is not cached or partially cached, a disk read is required (line 17). 
			Periodical flushing is called once again, but not time-limited since 
			data flushing and disk read are sequential, and the flushing time is 
			added to simulated time (line 18).
			Finally, data is read from disk to cache and managed by MemoryManager, 
			disk read time estimated by the storage model is added to 
			total simulated run time (line 19-20).

@@

			To validate our simulation model, we create a simple 
			simulator which is independent to simulation frameworks and libraries. 
			This enables us to evaluate the accuracy and correctness of our 
			model in a simple use case before integrating it to SimGrid. 
			Since the simulator does not use any storage model, we simulate the 
			I/O time in memory as follow:

			\begin{align*}
				& t_{mr} = D / r_m \\ 
				& t_{mw} = D / w_m\
			\end{align*}

			where:
			\begin{itemize}
				\item $t_{mr}$ is the time to read data from memory
				\item $t_{mw}$ is the time to write data to memory
				\item $D$ is the amount of data to read/write
				\item $r_m$ is the memory read bandwidth
				\item $w_m$ is the  memory write bandwidth
			\end{itemize}

			This simulator simulates a single-threaded pipeline running on a system 
			with a single core CPU, one local storage device and all input and 
			output files are stored locally. The results from the simulator is compared 
			and validated with the results from a real pipeline running on
			a real system.

			Having our model validated, we create simulators for different use cases 
			using the current version of SimGrid and the SimGrid version that is 
			extended with our model. We leverage Wrench framework, which is 
			built on top of SimGrid to simulate our pipelines and system.
			Then, we compare the results of the simulators with
			original SimGrid and extended SimGrid with the results of real
			pipelines on a real system.

			In this work, we use Python 3.7 to implement the simple
			simulator, SimGrid 3.25 and Wrench 1.6 for SimGrid simulators. 
			SimGrid source code is available at 
			\url{https://framagit.org/simgrid/simgrid}, and Wrench is provided on
			github at \url{https://github.com/wrench-project/wrench}.

@@

			When designing experiments, our goal is to evaluate our simulation model 
			in single-threaded and multi-threaded applications which access data on 
			on different file system types. 
			To do that, we create a pipeline of sequential tasks, each task 
			reads an input file, increases every byte of the input, and writes the 
			output to disk. The output of the previous task is the input of 
			the next task. We also adopt an use case in real applications and 
			to evaluate the applicability of our simulation model.

			The simplest scenario is a single-threaded application, where memory 
			bandwidth and disk bandwidth are not shared with another thread. 
			This allows us to compare the detailed results in terms of read/write time, 
			memory states after every single task and ,more importantly, validate our 
			simulation model.

			For multi-threaded applications, we do the experiment with a varying 
			number of concurrent pipelines running on a multi-core host 
			and writing to the same local storage device. 
		    By doing so, we can assess the performance of our model in the case  
		    of concurrent I/O with shared bandwidth on a local storage device.

		    Since different storage types should also be taken into account, 
		    we conduct the next experiment with the same scenario as 
		    in the multi-threaded experiment, except that files are stored on a 
		    shared file system instead of local disk. 
		    In this way, we can not only evaluate our simulation model on I/O 
		    with shared file system, but also compare the 
		    performance of the simulator on different storage types.

		    Finally, we adopt a real pipeline in a real neuroimaging applications. 
		    We simulate the pipeline with a simulated workflow in SimGrid 
			and compare the simulation results with the real results. 
			Because our work focuses on I/O time, we assume that CPU time is 
			correctly modeled and use the CPU time measured in the real pipelines 
			to setup our simulated workflows.

			We use the cluster of \textit{Big Data Infrastructure for Neuroimaging Lab} 
			at \textit{Concordia University} to conduct our experiments. The cluster 
			consists of one login node which is the control node, 8 compute nodes 
			and 4 storage nodes connected with two network switches. The login node 
			has one Intel(R) Xeon(R) Gold 6130 CPU @ 2.10GHz, 128GiB of RAM, 1.8TB 
			of storage of XFS file system, 13GB of tmpfs file system and 385 TB of 
			Lustre shared file system. Each compute node has two 16 cores Intel(R) 
			Xeon(R) Gold 6130 CPU @ 2.10GHz, 256 GB of RAM and 6 SSDs, 450GB each 
			with XFS file system, 378GB of tmpfs and 126GB of devtmpfs file system.
			Lustre file system is configured with one metadata target with 854GB 
			of storage, 44 object storage targets with 8.7TB of storage each. 
			The cluster is run on CentOS 8.1 with the Slurm Workload Manager installed. We use 
			\textbf{\textit{atop}} and \textbf{\textit{collectl}} as tools to monitor 
			and collect data of memory, page cache status and disk throughput on 
			the cluster. The cluster nodes are connected with ... 
			\textcolor{red}{[network description here]}

			\subsubsection{Single-threaded evaluation}

@@

	\section{Discussion and Future Work}
		\begin{itemize}
			\item Sensitivity of the simulator on the variation of memory and disk bandwidth. 
		\end{itemize}
\bibliographystyle{plain}
\bibliography{citation}

>>>>

		\subsection{Page cache}
			\begin{itemize}
				\item What is page cache? How it works \cite{linuxdev3rd2010}. Effects and importance of page cache.
				\item Introduce some existing strategies with some highlighted pros and cons.
				\item Current implementation in Linux and some reasons why it is chosen to be implemented (implementation complexity, effectiveness, overhead, etc) \cite{linuxdev3rd2010}
				\item \tristan{LRU lists are mentioned in the next section, they should be described here.}
			\end{itemize}

		\subsection{Simulators}
			\begin{itemize}
				\item Discuss some existing methods, simulation frameworks to conduct HPC experiments. Compare pros and cons (accuracy, simulation time, usability) of some simulators (SimGrid, GridSim).
				\item Related development: RAM energy consumption \cite{gill2019} \cite{ouarnoughi2017} 
				\item Discuss the pros of SimGrid and the reasons why we chose it to extend. (Section 2.2.2 in \cite{casanova2014})
				\item \tristan{Mention the status of storage simulation in simulators, so that we understand from Fig 1 that storage devices are available}
			\end{itemize}

	\section{Method}
		In this section, we present our approach to model file read/write,
		memory I/O, cache eviction and data flushing mechanisms implemented in
		the Linux kernel. We also detail the design of our simulators and their
		implementation. Finally, we describe experimental scenarios to evaluate
		our simulation model on real applications using a standalone Python
		prototype, the current SimGrid simulator, and our extension of SimGrid.

@@

            We separate our simulation model in two components, the IO
			Controller and the Memory Manager, which together simulate Linux
			kernel I/Os (Figure~\ref{fig:interaction}). The Memory Manager
			simulates memory I/O, flushing, and cache eviction, whereas the IO
			Controller simulates file reads and writes. Simulated applications
			can simply interact with the IO Manager instead of calling simulated
			storage directly as is the case with current simulators.

@@

			We model memory as a storage device, characterized with a capacity,
			a read bandwidth and a write bandwidth in most simulators
			\tristan{are the read and write bandwidths distinguished in simgrid?
			we should also talk about latency}. We refer to existing simulation
			models for storage devices, to simulate bandwidth sharing for
			parallel accesses \tristan{we should refer to related work, see
			comment there}.

			We introduce the concept of a data block as a unit to represent data
			cached in memory. A data block is a subset of file pages stored in
			page cache that were accessed in the same read or write
			operation. A data block
			has information about file name, block size, last access time, and a
			dirty flag that represents whether the data is clean (0) or dirty
			(1). A given file can have multiple data blocks in page cache. In
			addition, a data block can be split into an arbitrary number of
			smaller blocks, and data blocks can be merged together.
			\tristan{I reformulated this paragraph, please check}

			We simulate the kernel LRU lists of file pages
			with two lists of data blocks: an active list and 
			an inactive list, ordered by last access time (earliest first, see Figure~\ref{fig:lrulist}).
			As in the kernel, our simulator keeps the size of the active list under
			twice the size of the inactive list by moving least recently 
			used data blocks from the active list to the inactive list. 
			Modeling page cache LRU lists as lists of data blocks reduces the
			overhead of the simulator, as data blocks are obviously less
			numerous than file pages, while preserving the accuracy in I/O time
			simulation \tristan{how do you know that, can you provide an argument?}.

@@

			\tristan{is this paragraph about read accesses or write accesses? I
			think you should make one for reads, and one for writes. The
			paragraph could start as follows: ``The simulated LRU lists are used
			as follows. When a file is accessed, \ldots ''} At the time when a
			file is accessed, some data of the file can be in cache or not. If
			accessed data is already cached, there are existing data blocks
			representing cached data in two page cache LRU lists. 
			As cached data is accessed again, these blocks are moved to 
			the active list, dirty blocks are merged into a bigger dirty block, 
			while clean data blocks are merged into another clean block. 
			If accessed data is not in cache, new blocks representing uncached data 
			are created and put into the top of the inactive list. 
			For more detail when uncached data is accessed, in the case of 
			reading file, as all uncached data is clean data, only one clean data 
			block is added to the inactive list.
			But in the case of writing uncached file data though cache, 
			this written data can be either dirty or clean. 
			Thus, at most two data blocks can be added to the inactive lists, 
			one is clean and one is dirty. 
			We also keep the size of the active list not larger than twice the size of 
			the inactive list as in the kernel. This is done by moving least recently 
			used blocks in the active list to the inactive list when the active list 
			grows. If only a part of a data block needs to be moved, 
			the block is split.

			Next, we simulate data flushing mechanism, which writes back 
			dirty data to disk. 
			The data flushing simulation function traverses the sorted inactive first, 
			and then the active list, looks for least recently used dirty blocks \tristan{, writes them to disk through the storage device model,} and 
			sets dirty flags of these blocks to 0 until the total flushed amount 
			reaches the amount to be flushed or there is no dirty data left in cache. 
			If the last flushed block is not entirely flushed, it is split into 
			two blocks, one that is flushed and one that remains dirty.
			The flushing time is simulated with storage model.

			For periodical flushing, our simulator searches in two page cache 
			LRU lists and flushes all the expired dirty data blocks. 
			A dirty data block is considered expired if the time from its last access 
			to current simulated time is longer than the predefined expire time. 
			Periodical flushing can be concurrent with cache read/write, 
			and sequential with disk read/write. When cache accesses and 
			periodical flushing are concurrent, flushing time is not added to simulated 
			time but the amount of flushed data is limited by flushing time. 
			When data is flushed in parallel with disk read/write, flushing time is 
			calculated by storage simulation model and total amount of data 
			to be flushed \tristan{This concurrency should be handled by the storage model, not the memory manager described here. 
			Rephrase the last sentences to explain this.}.

@@

            \tristan{very good writing Dzung, it reads very well now.}

@@

			Simulated applications can simply request for a file read 
			or a file write by calling the IO Controller instead of 
			the storage simulation models. 
			\tristan{this should move, not sure where for now: Because every computer has its own memory and system configurations, 
			one IO Controller object and one Memory Manager object are created 
			for each simulated machine.}

			To read or write a file, a simulated application sends a request to the 
			IO Controller instance on the node where the requested file is stored.
			Based on the memory status in Memory Manager, the IOController 
			orchestrates cache reads and writes, disk reads and writes, flushing, cache eviction 
			 and returns to the simulated application.

@@

			The algorithm to simulate file reads is described in 
			Algorithm~\ref{alg:read} \tristan{you should now remove the incrementation of simulation time, as the storage models will do that.
			Essentially, we neglect kernel time and assume that time is entirely spent in IO. It will simplify the algorithms further, which is also elegant. If you 
			agree, please revise the algorithm and its description accordingly, and do the same for algorithm 2.
			}.  
			In Linux systems with write-back storage devices, data can be either read 
			from cache with memory bandwidth or read from disk with disk bandwidth. 
			Therefore, total read time can be considered as a linear function 
			of the read time with each of these bandwidths, 
			enabling us to generalize reading process as two separate phases, 
			cache read and disk read. 
			When a simulated application reads a file, 
			it sends a file read request to IO Controller. 
			First, if there  is not enough memory available to store two
			copies of the file (one in cache, one in anonymous memory), the
			Memory Manager is called to flush dirty data to disk (line 10).
			This flushing is complemented by eviction by the Memory Manager (line 11). 
			Next, if the file is cached, either partially or entirely, the Memory Manager is 
			called to read and update the corresponding data blocks in cache (line 13). 
			During cache read, periodical flushing is called to flush dirty data if needed 
			and limited to cache read time \tristan{unclear, reword} (line 14).
			Cache read time is then added to total simulated time (line 15) \tristan{this should be part of the storage model}. 
			If file is not cached or partially cached, a disk read is required (line 17). 
			Periodical flushing is called once again, but not time-limited since 
			data flushing and disk read are sequential, and the flushing time is 
			added to simulated time (line 18).
			Finally, data is read from disk to cache and managed by MemoryManager, 
			disk read time estimated by the storage model is added to 
			total simulated run time (line 19-20).

@@

			To validate our simulation model, we create a simple prototype
			simulator independently of existing simulation frameworks and libraries. 
			This enables us to evaluate the accuracy and correctness of our 
			model in a simple scenario before integrating it in the more complex SimGrid environment. 
			In this prototype we use the following basic storage model, used for both memory and disk: 
			\begin{align*}
				& t_{mr} = D / r_m \\ 
				& t_{mw} = D / w_m\
			\end{align*}

			where:
			\begin{itemize}
				\item $t_{mr}$ is the time to read data from memory
				\item $t_{mw}$ is the time to write data to memory
				\item $D$ is the amount of data to read/write
				\item $r_m$ is the memory read bandwidth
				\item $w_m$ is the  memory write bandwidth
			\end{itemize}			
			\tristan{if this applies equally to memory and disk, use ``device'' instead of ``memory''}

			Since bandwidth sharing is not simulated, this prototype doesn't support concurrency: it is limited 
			to single-threaded pipelines running on systems 
			with a single-core CPU. \tristan{the following aren't resulting from the lack of bandwidth sharing simulation, these are more general limitations, I think we 
			should remove them: , a single local storage device, and all input and 
			output files are stored locally.} We use it in a first validation of our simulation model,
			against a real sequential pipeline running on
			a real system.

			Having our model validated, we create simulators for different use cases 
			using the current version of SimGrid and the SimGrid version that is 
			extended with our model. To simulate our pipelines and system, we leverage the Workflow Management System Simulation Workbench (WRENCH~\cite{wrench}), a framework  
			built over SimGrid.
		    We compare the results of the simulators with
			original SimGrid and extended SimGrid with the results of real
			pipelines on a real system \tristan{this will have to be updated with a description of extended SimGrid, 
			you should add a placeholder for this description.}.

			We use Python 3.7 to implement the simple simulator, SimGrid 3.25
			and Wrench 1.6 for SimGrid simulators. SimGrid source code is
			available at \url{https://framagit.org/simgrid/simgrid}, and WRENCH
			is at \url{https://github.com/wrench-project/wrench}.
			\tristan{You should also add the URL of your Python prototype}

@@

			The goal of our experiments is to evaluate our write-back cache
			simulation in single-threaded and multi-threaded applications
			accessing data on different types of file system. We use a pipeline
			of sequential tasks where each task reads an input file, increments
			every byte of the input to emulate real processing and avoid caching
			effects, and writes the result to disk. The output of the previous
			task is the input of the next task. We also use a real application pipeline, to evaluate the applicability of our
			simulation model \tristan{add a placeholder to describe the real pipeline here}.

			The simplest execution scenario is single-threaded, where memory 
			bandwidth and disk bandwidth are dedicated. 
			This allows us to compare the detailed results in terms of read/write time, 
			memory states after every single task and, more importantly, validate our 
			simulation model \tristan{last sentence is convoluted, reword}.

			For multi-threaded applications, we vary the number of concurrent
			pipelines running on a multi-core host and writing to the same local
			disk. In this way, we evaluate our model with concurrent I/Os, when
			the device bandwidth is shared.

		    Since different storage types should also be taken into account, 
		    we conduct the next experiment with the same scenario as 
		    in the multi-threaded experiment, except that files are stored on a 
		    shared file system instead of local disk.

		    Finally, we consider a real pipeline from the neuroimaging domain. 
		    We simulate the pipeline with a simulated workflow in SimGrid 
			and compare the simulation results with the real results. 
			Because our work focuses on I/O time, we assume that CPU time is 
			correctly modeled and use the CPU time measured in the real pipelines 
			to setup our simulated workflow \tristan{the pipeline should be described, including the workflow engine if it's Dask.}.

			We use our dedicated cluster hosted at Concordia University to conduct the experiments. The cluster 
			consists of one login node, 8 compute nodes 
			and 4 storage nodes connected with two network switches. The login node 
			has one Intel(R) Xeon(R) Gold 6130 CPU @ 2.10GHz, 128GiB of RAM, 1.8TB 
			of storage of XFS file system, 13GB of tmpfs file system and 385 TB of 
			Lustre shared file system. Each compute node has two 16 cores Intel(R) 
			Xeon(R) Gold 6130 CPU @ 2.10GHz, 256 GB of RAM and 6 SSDs, 450GB each 
			with XFS file system, 378GB of tmpfs and 126GB of devtmpfs file system.
			Lustre file system is configured with one metadata target with 854GB 
			of storage, 44 object storage targets with 8.7TB of storage each. 
			The cluster is run on CentOS 8.1 with the Slurm Workload Manager installed. We use 
			\textbf{\textit{atop}} and \textbf{\textit{collectl}} as tools to monitor 
			and collect data of memory, page cache status and disk throughput on 
			the cluster. The cluster nodes are connected with ... 
			\textcolor{red}{[network description here]}
			\tristan{mention the number of disks on all nodes. Maybe add a diagram.}

			\tristan{I don't think you need an intro paragraph for each experiment, as you did above, AND then subsections. I'd just make a single paragraph or sub-section.}
			\subsubsection{Single-threaded evaluation}

@@

	\section{Discussion and Future Work}
		\begin{itemize}
			\item Sensitivity of the simulator on the variation of memory and disk bandwidth. 
		\end{itemize}
	\section{CFI for cluster}
\bibliographystyle{plain}
\bibliography{citation}
